---
title: "Ezra Miller Combined Plot"
author: "Matthew Bustos"
date: "2026-05-12"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Plot for The final query in the .sql file. Combines 3 different time series: monthly revenue, monthly movie frequency (how many movies Ezra Miller was involved in), and monthly search interest. Each of these values were scaled by dividing its current value with the max value, transformed into a percentage. For example, if Ezra Miller was in 1 movie during the month of June 2016, then that scaled value would be 0.5 since the max amount of movies he was involved at a time was 2 (1/2 * 100).

```{r}

library(DBI)
library(RMariaDB)
library(ggplot2)
library(dplyr)
library(tidyr)

# Create connection object
con <- dbConnect(
  RMariaDB::MariaDB(),
  host     = "localhost",      # Or "localhost" if the server is on your machine
  port     = 3306,             # Default MySQL port
  user     = "root",  # Usually "root" for local setups
  password = "sesame80", # do not put password in here. Github etc. 
  dbname   = "sem_project"
)

library(ggplot2)

plot_data <- dbGetQuery(con, "WITH monthly_search AS (
    SELECT
        DATE_FORMAT(trend_date, '%Y-%m-01') AS month_start,
        AVG(search_interest) AS avg_search_interest
    FROM ezra_search_trends
    GROUP BY month_start
), monthly_revenue AS (
    SELECT
        STR_TO_DATE(DATE_FORMAT(revenue_date, '%Y-%m-01'), '%Y-%m-%d') AS month_start,
        SUM(daily_revenue) AS total_monthly_revenue
    FROM ezra_daily_revenue
    GROUP BY month_start
), monthly_releases AS (
	SELECT
        DATE_FORMAT(release_date, '%Y-%m-01') AS month_start,
        COUNT(*) AS movies_released
    FROM ezra
    GROUP BY month_start
), combined AS (
    SELECT
        s.month_start,
        s.avg_search_interest,
        COALESCE(r.total_monthly_revenue, 0) AS total_monthly_revenue,
        COALESCE(m.movies_released, 0) AS movies_released
    FROM monthly_search s
    LEFT JOIN monthly_revenue r
        ON s.month_start = r.month_start
    LEFT JOIN monthly_releases m
        ON s.month_start = m.month_start
)
SELECT
    month_start,
    avg_search_interest,
    total_monthly_revenue,
    movies_released,
    ROUND(avg_search_interest / MAX(avg_search_interest) OVER () * 100, 2) AS search_index,
    ROUND(total_monthly_revenue / MAX(total_monthly_revenue) OVER () * 100, 2) AS revenue_index,
    ROUND(movies_released / MAX(movies_released) OVER () * 100, 2) AS movie_frequency_index
FROM combined
ORDER BY month_start;")

plot_data$month_start <- as.Date(plot_data$month_start)

plot_long <- plot_data %>%
  pivot_longer(
    cols = c(search_index, revenue_index, movie_frequency_index),
    names_to = "metric",
    values_to = "index_value"
  )

ggplot(plot_long, aes(x = month_start, y = index_value, color = metric)) +
  geom_line(linewidth = 1) +
  geom_vline(xintercept = as.Date("2022-06-01"), linetype = "dashed") +
  labs(
    title = "Ezra Miller: Search Attention vs Box Office Activity",
    subtitle = "Metrics are normalized to a 0–100 index for comparison",
    x = "Month",
    y = "0-100 Scaled Index",
    color = "Metric"
  ) +
  theme_minimal()
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
